CTA Proposal:\\SEGUE 1: An Unevolved Fossil Galaxy from the Early Universe

### 2021-03-04 Phys 311/CTA/Paper/paper.tex
update to aastex631

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.3
\documentclass{aastex63}

@@

In the three lowest metallicity stars (The top 3 blue lines) the abundance of iron (both Fe I and Fe II) is mostly indistinguishable
from the noise in the measurements. In the 3 stars with observable amounts of iron there was no correlation between increasing
iron abundance and increasing metallicity, indicated by the appearance of more spectral lines. This indicated that there was at most one or maybe two Type Ia supernova that enriched SEGUE. This
contrasts the trend found in galaxies from later where there would be a clear trend in increasing metallicity and increasing
iron abundance as they evolve alongside energetic supernovae events. Other indications of the age of SEGUE include enhanced
[$\alpha$/Fe] values found in all it's stars that are consistent with their birth cloud, and the low abundance of neutron-capture
elements. The consistent [$\alpha$/Fe] values in SEGUE 1 stars suggest that there were no energetic supernovae events that enriched
the birth gas cloud during the star formation events. The low abundance of neutron-capture elements in SEGUE's non-binary stars,
which total to less than \(\sim 10^{-7} M_{\odot}\) for each element, indicate that there were no neutron-capture element producing
process, which produce \(\sim 10^{-4} M_{\odot}\) of neutron-capture elements per event, that occurred during the star formation phase.

>>>>

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.3.1
\documentclass{aastex631}

@@

In the three lowest metallicity stars (The top 3 blue lines) the abundance of iron (both Fe I and Fe II) is mostly indistinguishable
from the noise in the measurements. In the 3 stars with observable amounts of iron there was no correlation between increasing
iron abundance and increasing metallicity, indicated by the appearance of more spectral lines. This indicated that there was at most
one or maybe two Type Ia supernova that enriched SEGUE. This
contrasts the trend found in younger galaxies where there would be a clear trend in increasing metallicity and increasing
iron abundance in the stellar population as they evolve alongside energetic supernovae events.

Other indications of the age of SEGUE include enhanced [$\alpha$/Fe] values found in all it's stars that are consistent with the birth 
cloud, and the low abundance of neutron-capture
elements. The consistent [$\alpha$/Fe] values in SEGUE 1 stars suggest that there were no energetic supernovae events that enriched
the birth gas cloud during the star formation events. The low abundance of neutron-capture elements in SEGUE's non-binary stars,
which total to less than \(\sim 10^{-7} M_{\odot}\) for each element, indicate that there were no neutron-capture element producing
process, which produce \(\sim 10^{-4} M_{\odot}\) of neutron-capture elements per event, that occurred during the star formation phase.
